NTM CT Scoring - Initial Agreement

### 2022-11-28 Stacey Martiniano/ntm_agreement.qmd
Update ntm_agreement.qmd
tidyverse styling

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    self-contained: true
editor: visual
---

```{r}
#| include: false
library(dplyr)
library(irr)
library(redcapAPI)
# Import data
api <- read.table("~/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",header = F)
rcon <- redcapConnection(url = "https://redcap.ucdenver.edu/api/",
                         token = api[1,1])
data = exportRecords(rcon)
# Make scorer IDs by initial
data$scorer = paste0(toupper(substr(data$reader_first_name,1,1)),
                     toupper(substr(data$reader_last_name,1,1)))
data = data %>% arrange(scan_id,scorer) %>% filter(scan_id>2) %>% 
  select(scorer,scan_id,bronchiectasis_rul:atelectasis___6)
```

# Scan 3

@@

```{r}
# Get relevant columns and prepare for Fleiss' kappa calculation
bronch = data %>% filter(scan_id==3) %>% 
  select(scorer,bronchiectasis_rul:bronchiectasis_lll)
rows = as.character(label(bronch)[-1])
cols = bronch$scorer
bronch = data.frame(t(bronch[,-1]))
rownames(bronch) = rows
colnames(bronch) = cols
```

>>>>

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 5
    toc-float: true
    self-contained: true
    fig-height: 8
    fig-width: 10
editor: visual
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("~/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
  header = F
)
rcon <- redcapConnection(
  url = "https://redcap.ucdenver.edu/api/",
  token = api[1, 1]
)
data <- exportRecords(rcon, labels = F)
data <- data.frame(lapply(data, as.character))
# Make scorer IDs by initial
data$scorer <- paste0(
  toupper(substr(data$reader_first_name, 1, 1)),
  toupper(substr(data$reader_last_name, 1, 1))
)
# Select relevant columns, convert to long data
data <- data %>%
  arrange(scan_id, scorer) %>%
  filter(scan_id > 2) %>%
  select(scorer, scan_id, bronchiectasis_rul:atelectasis___6)
data <- data %>%
  pivot_longer(bronchiectasis_rul:atelectasis___6,
    names_to = c("feature", "location"),
    names_pattern = "(.*)_(.*)$"
  ) %>%
  mutate(
    feature = gsub("__", "", feature),
    feature = str_to_title(gsub("_", " ", feature))
  )
data$location <- factor(data$location,
  levels = c("1", "2", "3", "4", "5", "6", "ling", "lll", "lul", "rll", "rml", "rul"),
  labels = c("RUL", "RML", "RLL", "LUL", "Ling", "LLL", "Ling", "LLL", "LUL", "RLL", "RML", "RUL")
)
data$value <- factor(data$value, levels = c("Checked", "Unchecked", "Absent", "Cylindric", "Varicose"))
vals <- levels(data$value)
# One column per scorer
data <- data %>% pivot_wider(names_from = scorer, values_from = value)
# Find disagreements
data$disagree <- !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n <- length(vals)
name <- "Accent"
colors <- brewer.pal(n, name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

# All disagreements

The table below is sortable and searchable, and includes only the features and locations where there was some disagreement.

```{r}
# Table
data %>%
  filter(disagree == T) %>%
  select(-disagree) %>%
  datatable(., rownames = F)
```
# Plots

## All scans

```{r}
data %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_grid(rows = vars(scan_id), cols = vars(feature))
```

## Scan 3

```{r}
scan <- 3
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

## Scan 4

```{r}
scan <- 4
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

## Scan 5

```{r}
scan <- 5
data %>%
  filter(scan_id == scan) %>%
  select(feature, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~feature)
```

# Agreement by Feature

## Atelectasis

```{r}
feat <- "Atelectasis"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

@@

```{r}
feat <- "Bronchiectasis"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cavity

```{r}
feat <- "Cavity"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Consolidation

```{r}
feat <- "Consolidation"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Cyst

```{r}
feat <- "Cyst"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Ground Glass

```{r}
feat <- "Ground Glass"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Mucoid Impaction

```{r}
feat <- "Mucoid Impaction"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Nodule

```{r}
feat <- "Nodule"
# Statistic
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.

## Tree in Bud

```{r}
feat <- "Tree In Bud"
# Statistics
k <- data %>%
  filter(feature == feat) %>%
  select(AF:JW) %>%
  kappam.fleiss(.)
ka <- round(k$value, 3)
p <- format.pval(k$p.value, eps = 0.001, digits = 3)
# Plot
data %>%
  filter(feature == feat) %>%
  select(scan_id, location, AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(., aes(x = name, y = location, fill = value)) +
  geom_tile(color = "black") +
  theme_bw() +
  labs(fill = "", x = "Scorer", y = "Location") +
  custom_colors +
  facet_wrap(~scan_id)
```

Fleiss' Kappa for multiple raters was `r ka` (p: `r p`) across all scans.
